---
title: "Ranking de Clientes - Testing"
author: "GSK"
date: "Thursday, September 17, 2015"
output: html_document
---

#### Set up

Input data tables are:

```{r echo = F, results='markup'}

# Params
CODE_DIR       = 'C:/Users/AAB330/Google Drive 2/Business Cases/Rosental/BI/StockBroker_code' 
DATA_DIR       = '../StockBrokerData'
DATA_ORIGIN    = '../StockBroker_rar'
ROBJECTS       = 'DataFiles.RData'

# Set up
setwd(CODE_DIR)
source('EDA_ETL_AuxFuncts.R')
load(ROBJECTS, verbose = T)

``` 

#### Parameters: Period and number of customers
Note that these parameters applies to all tests except for AuM Ranking.

```{r echo = F, results ='markup', collapse = TRUE}

(FromDate =  '01-01-2002')     # Change Start date here
(ToDate   =  '31-12-2015')     # Change End date here
(N        =   15)              # Change nr of customers in ranking here

FromDate <- as.Date(x = FromDate, format = '%d-%m-%Y')
ToDate   <- as.Date(x = ToDate, format = '%d-%m-%Y')

```


#### Test Comisiones x Boletos

```{r echo = T, results = 'markup'}

# Filters
Oper <- OPER[OPER$OperFecAnul == '1753-01-01', ]
Oper <- Oper[Oper$OperComiCMonto != 0, ]

# Join tables OPER and PERSONAS
Oper <- Oper[Oper$OperFecCon >= FromDate & Oper$OperFecCon <= ToDate, ]
Comi <- merge(Oper, PERSONAS, by = 'ComiCodigo')
Comi <- Comi[, c('ComiCodigo', 'OperFecCon', 'OperComiCMonto', 
                 'PersTitular', 'PersApellido', 'PersNumeroDoc', 'PersPorPar')]

# Compute each person's total comission 
Comi$Monto <- Comi$OperComiCMonto * (Comi$PersPorPar / 100)  
ComiPers <- aggregate(x = Comi$Monto,
                      by = list(PersApellido = Comi$PersApellido, 
                                PersNumeroDoc = Comi$PersNumeroDoc),
                      sum)
names(ComiPers)[3] <- 'Monto'

# Create accumulator to compute Total comissions
TotPers <- ComiPers 

# plot Ranking
plot_TopN(ComiPers, N, 'Comisiones por Boletos')

```


#### Test Comisiones x Dividendos

```{r echo=T, results='markup'}

# Filters

Divra4 <- DIVRA4[DIVRA4$TiCdId == 4, ]
Divra4 <- Divra4[Divra4$DivComMonto > 0, ]

# Join tables DIVRA and DIVRA4 to get date
Divra44 <- merge(Divra4, DIVRA, by = 'DRAID')
Divra44 <- Divra44[, c(names(Divra4), 'DRAFecPos')]
Divra44 <- Divra44[Divra44$DRAFecPos >= FromDate & Divra44$DRAFecPos <= ToDate, ]

# Join tables DIVRA44 and PERSONAS to get Personal data
Comi <- merge(Divra44, PERSONAS, by = 'ComiCodigo')
Comi <- Comi[, c(names(Divra44), 'PersTitular', 'PersApellido', 
                 'PersNumeroDoc', 'PersPorPar')]

# Compute each person's total comission 
Comi$Monto <- Comi$DivComMonto * (Comi$PersPorPar / 100)  
ComiPers <- aggregate(x = Comi$Monto,
                      by = list(PersApellido = Comi$PersApellido, 
                                PersNumeroDoc = Comi$PersNumeroDoc),
                      sum)
names(ComiPers)[3] <- 'Monto'

# add to accumulator
TotPers <- rbind(TotPers, ComiPers)
TotPers <- aggregate(x = TotPers$Monto,  
                     by = list(PersApellido  = TotPers$PersApellido, 
                               PersNumeroDoc = TotPers$PersNumeroDoc), 
                     sum)
names(TotPers)[3] <- c('Monto')

# plot Ranking
plot_TopN(ComiPers, N, 'Comisiones por Dividendos')

```


#### Test Comisiones x Mant de Cta 

```{r echo=T, results='markup'}

# Filters
CtaCte <- CUENTACORRIENTE[CUENTACORRIENTE$CompId == 5, ]

# Join tables CtaCte and PERSONAS to get Personal data
CtaCte <- CtaCte[CtaCte$CuCoFecConcertacion >= FromDate & 
                     CtaCte$CuCoFecConcertacion <= ToDate, ]
Comi <- merge(CtaCte, PERSONAS, by = 'ComiCodigo')
Comi <- Comi[, c(names(CtaCte), 'PersTitular', 'PersApellido', 
                 'PersNumeroDoc', 'PersPorPar')]

# Compute each person's total comission 
Comi$Monto <- Comi$CuCoImporte * (Comi$PersPorPar / 100)  
ComiPers <- aggregate(x = Comi$Monto,
                      by = list(PersApellido = Comi$PersApellido, 
                                PersNumeroDoc = Comi$PersNumeroDoc),
                      sum)
names(ComiPers)[3] <- 'Monto'

# add to accumulator
TotPers <- rbind(TotPers, ComiPers)
TotPers <- aggregate(x = TotPers$Monto,  
                     by = list(PersApellido  = TotPers$PersApellido, 
                               PersNumeroDoc = TotPers$PersNumeroDoc), 
                     sum)
names(TotPers)[3] <- c('Monto')

# plot Ranking
plot_TopN(ComiPers, N, 'Comisiones por Mant. Cta.')

```


#### Test Comisiones x ND y NC 

```{r echo=T, results='markup'}

# Filters
CompMov <- COMPMOV[COMPMOV$CompId == 18 | COMPMOV$CompId == 19, ]
CompMov <- CompMov[CompMov$CompFecAnul == '1753-01-01', ]

# Join tables CompMov and PERSONAS to get Personal data
CompMov <- CompMov[CompMov$CompFecha >= FromDate & CompMov$CompFecha <= ToDate,]
Comi <- merge(CompMov, PERSONAS, by = 'ComiCodigo')
Comi <- Comi[, c('ComiCodigo', 'CompId','CompFecha','CompImporte', 'PersTitular', 'PersApellido', 
                 'PersNumeroDoc', 'PersPorPar')]

# Reverse sign of NCs
Comi[Comi$CompId == 19, 'CompImporte'] <- Comi[Comi$CompId == 19, 'CompImporte'] * (-1)

# Compute each person's total comission 
Comi$Monto <- Comi$CompImporte * (Comi$PersPorPar / 100)  
ComiPers <- aggregate(x = Comi$Monto,
                      by = list(PersApellido = Comi$PersApellido, 
                                PersNumeroDoc = Comi$PersNumeroDoc),
                      sum)
names(ComiPers)[3] <- 'Monto'

# add to accumulator
TotPers <- rbind(TotPers, ComiPers)
TotPers <- aggregate(x = TotPers$Monto,  
                     by = list(PersApellido  = TotPers$PersApellido, 
                               PersNumeroDoc = TotPers$PersNumeroDoc), 
                     sum)
names(TotPers)[3] <- c('Monto')

# plot Ranking
plot_TopN(ComiPers, N, 'Comisiones por ND y NC')
          
```

#### Total Ingresos por Comisiones

```{r echo = T, results = 'markup'}
plot_TopN(TotPers, 15, 'Total de Ingresos por Comisiones')
```

#### Test Ranking de AuM  

##### AuM Parameters: Period and number of customers

```{r echo = F, results ='hold'}

(FromDate =  '01-01-2015')     # Change Start date here
(ToDate   =  '31-12-2015')     # Change End date here
(N        =   15)              # Change nr of customers in ranking here

FromDate <- as.Date(x = FromDate, format = '%d-%m-%Y')
ToDate   <- as.Date(x = ToDate, format = '%d-%m-%Y')

```

##### AuM Ranking Computation

```{r echo=T, results='markup'}

# Filters
Operico <- OPERICO[OPERICO$ICoFecha >= FromDate & OPERICO$ICoFecha <= ToDate,]

# Join tables Operico and PERSONAS to get Personal data
Posi <- merge(Operico, PERSONAS, by = 'ComiCodigo')
Posi <- Posi[, c(names(Operico)[1:3], 'PersTitular', 'PersApellido', 
                 'PersNumeroDoc', 'PersPorPar')]

# Compute each person's net posicion 
Posi$Monto <- Posi$ICoPosGlb * (Posi$PersPorPar / 100)  
PosiPers <- aggregate(x = Posi$Monto,
                      by = list(PersApellido = Posi$PersApellido, 
                                PersNumeroDoc = Posi$PersNumeroDoc),
                      sum)
names(PosiPers)[3] <- 'Monto'

# plot Ranking
plot_TopN(PosiPers, N, 'Assets under Management')
          
```

